Model Samples Processing

### 2020-02-12 stats/model_sample_processing.Rmd
update sample processing

model <- bind_rows(
 fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 1),
fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 2), 
fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 3),
 fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain5.csv",header = T)%>%mutate(chain = 4),
 fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain6.csv",header = T)%>%mutate(chain = 5)
)

@@

saveRDS(item_params, "../saves/item_params.rds")

@@

saveRDS(global_params, "../saves/global_params_2.rds")

@@

saveRDS(item_sigma, "../saves/item_sigma_2.rds")

@@

saveRDS(model_pred_prag, "../saves/model_pred_prag_2.rds")

model_pred <- model %>%
  filter(a == "modelPrediction",
         b == "global")%>%
  select(-a, -h)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         item = e,
         age = f, 
         pred = g)

saveRDS(model_pred, "../saves/model_pred_global_2.rds")

model_pred_flat <- model %>%
  filter(a == "modelPrediction",
         b == "flat")%>%
  select(-a, -h)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         item = e,
         age = f, 
         pred = g)

saveRDS(model_pred_flat, "../saves/model_pred_flat_2.rds")

model_pred_prior <- model %>%
  filter(a == "modelPrediction",
         b == "prior")%>%
  select(-a, -h)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         item = e,
         age = f, 
         pred = g)

saveRDS(model_pred_prior, "../saves/model_pred_prior_2.rds")

>>>>

model <- bind_rows(
 fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain1.csv",header = T)%>%mutate(chain = 1),
 fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain2.csv",header = T)%>%mutate(chain = 2),
 read("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain3.csv",header = T)%>%mutate(chain = 3),
  fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 4),
  fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain5.csv",header = T)%>%mutate(chain = 5),
  fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain6.csv",header = T)%>%mutate(chain = 6)
)

@@

saveRDS(item_params, "../saves/item_params_fb.rds")

@@

saveRDS(global_params, "../saves/global_params_fb.rds")

@@

saveRDS(item_sigma, "../saves/item_sigma_fb.rds")

@@

saveRDS(model_pred_prag, "../saves/model_pred_prag_fb.rds")

# model_pred <- model %>%
#   filter(a == "modelPrediction",
#          b == "global")%>%
#   select(-a, -h)%>%
#   rename(model = b, 
#          parameter = c,
#          alignment = d,
#          item = e,
#          age = f, 
#          pred = g)
# 
# saveRDS(model_pred, "../saves/model_pred_global_2.rds")
# 
# model_pred_flat <- model %>%
#   filter(a == "modelPrediction",
#          b == "flat")%>%
#   select(-a, -h)%>%
#   rename(model = b, 
#          parameter = c,
#          alignment = d,
#          item = e,
#          age = f, 
#          pred = g)
# 
# saveRDS(model_pred_flat, "../saves/model_pred_flat_2.rds")
# 
# model_pred_prior <- model %>%
#   filter(a == "modelPrediction",
#          b == "prior")%>%
#   select(-a, -h)%>%
#   rename(model = b, 
#          parameter = c,
#          alignment = d,
#          item = e,
#          age = f, 
#          pred = g)
# 
# saveRDS(model_pred_prior, "../saves/model_pred_prior_2.rds")
